Hydra Battles in Coq

### 2020-11-20 doc/chapter-powers.tex
New library additions/AM.v (to certify)
new project in additions

\index{Projects}
\begin{project}
Study how  to compile efficiently such data structures.
\end{project}

@@

>>>>

\index{Projects}
\begin{project}
Study how  to compile efficiently such data structures.

\end{project}

@@

\index{Projects}
\begin{project}
Figures~\vref{fig:F3-as-dag} to \vref{fig:FFK} suggest that any computation following an Euclidean chain can be executed on a kind  of abstract machine with a "register'' and a stack, and only four operations:
\begin{itemize}
\item multiply the contents of the register by the top of the stack (and pop that stack),
\item raising the contents of the register to its square,
\item push the contents of the register into the stack,
\item swapping the two elements at the top of the stack.
\end{itemize}

In \coq{}, we define the instructions as the four constructors of an inductive type.

From Module~\href{../theories/html/hydras.additions.AM.html}{additions.AM}

\begin{Coqsrc}
(** basic instructions *)

Inductive instr : Set :=
  | MUL : instr
  | SQR : instr
  | PUSH : instr
  | SWAP : instr.

Definition code := list instr.

(* semantics *)
(*************)

Section Semantics.

 Variable M : Type.
 Variable mul : M -> M -> M.
 Variable one : M.

 Definition stack := list M.
 Definition config := (M * list M)%type.

 Fixpoint exec (c : code) (x:M) (s: stack) : option config :=
   match c, s with
     nil, _ => Some (x,s)
   | MUL::c, y::s => exec c (mul x y) s
   | SQR::c, s => exec c (mul x x) s
   | PUSH::c, s => exec c x (x::s)
   | SWAP::c, y::z::s => exec c x (z::y::s)
   | _,_ => None
   end.
\end{Coqsrc}

Please define an Euclidean chain generator using this data structure, and prove its correctness (partially solved in ~\href{../theories/html/hydras.additions.AM.html}{additions.AM}).
\end{project}
